### 2016-02-08 paper.tex
Minor changes in Sec 3

{\flushleft \em Constructing the MS-PUF. }
The MS-PUF is created by connecting outputs of DACs to 
input channels of an ADC. This creates loops between the processors
core, DACs, and ADCs as shown in Figure~\ref{fig:ms_puf}.
If there are $\alpha$ DACs and $\beta$ ADC channels in the device
(and $\alpha \le \beta$), then $\alpha$ such loops are made resulting 
in $\alpha$ feedback channels.
The PUFs challenge is a time-series pattern comprising of
$n$-bit digital values and a sequence of random channel identifiers.
The response is a time-series pattern comprising of $n$-bit digital 
values obtained from the ADC. The values for $n$ and $m$ are
respectively dependent on the DAC and ADC resolutions. Typically, $n = m$
for a device and have values 8, 12, 16, or 24.

@@

In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit 
reply from the ADC is the result of the $n$-bit DAC input $\mathbf T_j$ 
undergoing a conversion to analog followed by a reconversion to digital. 
Due to reasons such as quatification and ambient noise, the result ($r$)
would be different from $\mathbf T_j$ even if $m = n$.

@@

@@

two people speaking through a mobile phone. Sound is converted to an analog signal by the microphone, which is
then converted to digital form by an analog to digital converter(ADC) for transmission. In the other end, the digital
data is converted to analog by a digital to analog converter(DAC) and the speaker converts to audible sound. In this
digitalizing world, ADC and DAC modules are omnipresent in all devices. The main reason behind this is that all the input from
the external world is analog in nature and the device process everything digitally. This factor plays a key role in
the idea of using ADC and DAC components for PUFs. The ADC and DAC modules can be embedded inside the chip or outside the chip.

A set of hexadecimal values is passed to the DAC which converts it to its corresponding analog values which is again fed to ADC which converts back to digital value. So our challenge is an array of digital values which is fed to the DAC and response is calculated from the digital values output by the ADC of the device.The microscopic variations present in the ADC and DAC components gives rise to an unique response for each device for the same set of challenges. This mixed circuit based PUF is cost effective and very efficient as it does not require expensive hardware like arbiters and oscillators for digital electronic PUFs and can be easily reproducible unlike non electronic PUFs. Moreover, ADC and DAC components are ubiquitous in modern digital devices and can be modified easily with little effort and integrated effortlessly into the current crop of devices.

>>>>

\subsection{Constructing the MS-PUF}
The MS-PUF is created by connecting outputs of DACs to 
input channels of an ADC. This creates loops between the processors
core, DACs, and ADCs as shown in Figure~\ref{fig:ms_puf}.
If there are $\alpha$ DACs and $\beta$ ADC channels in the device
(and $\alpha \le \beta$), then $\alpha$ such loops are made resulting 
in $\alpha$ feedback channels.
The PUFs challenge is a time-series pattern comprising of
$n$-bit digital values and a sequence of random channel identifiers.
The response is a time-series pattern comprising of $n$-bit digital 
values obtained from the ADC. The values for $n$ and $m$ are
respectively dependent on the DAC and ADC resolutions. Typically, $n = m$
for a device and have values 8, 12, 16, or 24.

@@

{\flushleft \em Variations in the MS-PUF Response.}
In every iteration of Algorithm~\ref{algo:puf_sw}, $r$, the $m$-bit 
reply from the ADC is the result of the $n$-bit DAC input $\mathbf T_j$ 
undergoing a conversion to analog followed by a reconversion to digital. 
Due to reasons such as quatification and ambient noise, the result ($r$)
would be different from $\mathbf T_j$ even if $m = n$.

@@

{\flushleft \em Preventing Modeling Attacks.}

\subsection{A Formal Model for MS-PUFs}

\subsection{xxx}

@@
